Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Paper
Fixed Error label to Best-found error average

        For each experiment, we ran 30 independent executions per algorithm and
        dimensions specified. We recorded the following results: best found error,
        standard deviation, total number of evaluations, and total elapsed time (in
        seconds). The labels used on the results of our summarized experiments tables
        are the following:

        \begin{itemize}
            \item   Error:       is the best found error (or best solution).
            \item   St-Dev:      is the standard deviation calculated from the error. 
            \item   Evals.:      is the total number of evaluations the algorithm executed.
            \item   Time:        is the total elapsed or wall clock time, in seconds. 
        \end{itemize}

>>>>

        For each experiment, we ran 30 independent executions per algorithm and
        dimensions specified. We recorded the following results: best-found error average,
        standard deviation, total number of evaluations, and total elapsed time (in
        seconds). The labels used on the results of our summarized experiments tables
        are the following:

        \begin{itemize}
            \item   Error:       is the best-found error average.
            \item   St-Dev:      is the standard deviation calculated from the error. 
            \item   Evals.:      is the total number of evaluations the algorithm executed.
            \item   Time:        is the total elapsed or wall clock time, in seconds. 
        \end{itemize}
